The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-04 paper/ms.tex
bieryla changes

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element. Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage. From this observing run we have~33 unique targets with seismic \logg and spectra, the same as in the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. %Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

@@

\subsubsection{Chemical Compositions}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus. The chemical composition for the neutron-capture elements are shown in Fig.~\ref{fig:ncap}, and were derived in absolute terms rather than differentially with respect to Arcturus. The elemental abundance ratios were measured in order to determine the Galactic populations to which these stars belong. The metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution (Table~\ref{all_stars}) indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\

>>>>

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}. For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with a mean signal-to-noise ratio (SNRs) of $\sim 100$  per resolution element. Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage. From this observing run we have~33 unique targets with seismic \logg and spectra, the same as in the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. %Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

@@

\subsubsection{Chemical Compositions}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus. The chemical composition for the neutron-capture elements are shown in Fig.~\ref{fig:ncap}, and were derived in absolute terms rather than differentially with respect to Arcturus. The elemental abundance ratios were measured in order to determine the Galactic populations to which these stars belong. The metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution (Table~\ref{all_stars}) indicates that all stars are located within a few~kpc of the Sun and are not part of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
